---
title:  " Midterm Project 3"
author: Behzad FallahiFard
date:   last-modified
description: |
  [Midterm Project: Stat 445/545: Analysis of Variance],
  Stat 445/545, Spring 2023, Behzad FallahiFard, UNM
format:
  html:
    theme:            litera
    highlight-style:  atom-one
    page-layout:      full      # article, full   # https://quarto.org/docs/output-formats/page-layout.html
    toc:              false
    toc-location:     body  # body, left, right
    number-sections:  false
    self-contained:         false     # !!! this can cause a render error
    code-overflow:          scroll    # scroll, wrap
    code-block-bg:          true
    code-block-border-left: "#30B0E0"
    code-copy:              false     # true, false, hover a copy buttom in top-right of code block
---
```{r}
library(lmtest)
potato<-read.table("potato.txt",header=TRUE)
n<-nrow(potato)
n
```

```{r}
potato$regime<-factor(potato$regime,label=c("R","C"))
potato$variety<-factor(potato$variety,label=c("s1","s2"))
potato$temp<-factor(potato$temp,label=c("-4","-8"))
attach(potato)
potato[1:10,]
```

```{r}
tapply(leak,regime,mean)
tapply(leak,variety,mean)
tapply(leak,temp,mean)
```

```{r}
aggregate(leak~variety+regime+temp, data=potato, mean)
```

```{r, fig.width=12,fig.height=6}
#boxplot
par(mfrow=c(1,3))
boxplot(leak ~ variety,
        data = potato,
        xlab = "Variety",
        ylab = "Mean damage score for leaksynthesis")
boxplot(leak ~ regime,
        data = potato,
        xlab = "Regime",
        ylab = "Mean damage score for leaksynthesis")
boxplot(leak ~ temp,
        data = potato,
        xlab = "Temp",
        ylab = "Mean damage score for leaksynthesis")
```

```{r, fig.width=12,fig.height=7}
par(mfrow=c(1,1))
boxplot(leak ~ variety:regime:temp,
data = potato,
xlab = "V:R:T",
ylab = "Mean score of photo")
```

```{r, fig.width=10,fig.height=6}
interaction.plot(regime,variety:temp,leak,type='b',
col=1:4, pch=1:4)
```

```{r}
interaction.plot(regime,variety,leak,type='b',
col=1:2, pch=1:2,main="regime*variety")
potato2<-potato[temp==-4,]
nrow(potato2)
interaction.plot(potato2$regime,potato2$variety,potato2$leak,type='b',
col=1:2, pch=1:2,main="regime*variety, temp=-4")
```

#-------------------------------------------------------------------------
full

```{r}
##fit full model 
myfit<-lm(leak~variety*regime*temp,
contrasts = c(variety=contr.sum, regime=contr.sum,temp=contr.sum))
library(car)
Anova(myfit,type=3)
```

```{r}
qqPlot(myfit$residuals, las = 1, main="QQ Plot")
shapiro.test(myfit$resid)
plot(myfit$fitted,myfit$res,xlab="Fitted",ylab="Residuals")
leveneTest(myfit)
outlierTest(myfit)
```

```{r}
min(leak) # -1.11

leak2<- leak+2 #make response positive
myfit2<-lm(leak2~variety*regime*temp,contrasts = c(variety=contr.sum,
regime=contr.sum,temp=contr.sum))
library(MASS)
par(mfrow=c(1,1))
BC <- boxcox(myfit2, lambda = seq(-3, 3, length = 10))
```
#--------------------------------------------------------------
Full, log10
```{r}
log10_myfit<-lm(log10(leak2)~variety*regime*temp, 
                
contrasts = c(variety=contr.sum, regime=contr.sum,temp=contr.sum))
library(car)
Anova(log10_myfit,type=3)
```

```{r}
qqPlot(log10_myfit$residuals, las = 1, main="QQ Plot")
shapiro.test(log10_myfit$resid)
plot(log10_myfit$fitted,log10_myfit$res,xlab="Fitted",ylab="Residuals")
leveneTest(log10_myfit) #can not be appy for reduced models
#perform Breusch-Pagan test
#bptest(log10_myfit)
outlierTest(log10_myfit)
```
#-----------------------------------------------------------------
Full, (log10(leak2))^2
```{r}
## the second transformation 
#sq_log10_leak <- (log10(leak2)+1)^0.5 #+ (log10(leak2)+2)^0.5
sq_log10_leak <- (log10(leak2))^(1.5)
sq_log10_myfit<-lm(sq_log10_leak~variety*regime*temp,
contrasts = c(variety=contr.sum, regime=contr.sum,temp=contr.sum))
library(car)
Anova(sq_log10_myfit,type=3)
```


```{r}
qqPlot(sq_log10_myfit$residuals, las = 1, main="QQ Plot")
shapiro.test(sq_log10_myfit$resid)
plot(sq_log10_myfit$fitted,sq_log10_myfit$res,xlab="Fitted",ylab="Residuals")
leveneTest(sq_log10_myfit)
#bptest(sq_log10_myfit)
outlierTest(sq_log10_myfit)
```










#--------------------------------------------------------------

Comparing log10, ^2: (full)  vs (full-variety:regime:term)

```{r}
sq_log10_myfit_2 <- lm(sq_log10_leak ~ variety+regime+temp+variety:regime+variety:temp +temp:regime,
contrasts = c(variety=contr.sum, regime=contr.sum,temp=contr.sum))
anova(sq_log10_myfit,sq_log10_myfit_2)
```
According to the p-value log10_myfit_2 does not make difference with log10_myfit

```{r}
Anova(sq_log10_myfit_2,type=3)
```

```{r}
qqPlot(sq_log10_myfit_2$residuals, las = 1, main="QQ Plot")
shapiro.test(sq_log10_myfit_2$resid)
plot(sq_log10_myfit_2$fitted,sq_log10_myfit_2$res,xlab="Fitted",ylab="Residuals")
#leveneTest(log10_myfit) can not be appy for reduced models
#perform Breusch-Pagan test
bptest(sq_log10_myfit_2)
outlierTest(sq_log10_myfit_2)
```

#-------------------------------------------------------------------------
Comparing log10, ^2: (full-variety:regime:term)  VS  (full- variety:temp -variety:regime:term)

```{r}
sq_log10_myfit_3<- lm(sq_log10_leak~variety+regime+temp+variety:regime +temp:regime,
contrasts = c(variety=contr.sum, regime=contr.sum,temp=contr.sum))
anova(sq_log10_myfit_3,sq_log10_myfit_2)
```

According to the p-value log10_myfit_3 does not make difference with log10_myfit_2

```{r}
Anova(sq_log10_myfit_3,type=3)
```

```{r}
qqPlot(sq_log10_myfit_3$residuals, las = 1, main="QQ Plot")
shapiro.test(sq_log10_myfit_3$resid)
plot(sq_log10_myfit_3$fitted,sq_log10_myfit_3$res,xlab="Fitted",ylab="Residuals")
#leveneTest(sq_log10_myfit_2) can not be appy for reduced models
#perform Breusch-Pagan test
bptest(sq_log10_myfit_3)
outlierTest(sq_log10_myfit_3)
```

#-------------------------------------------------------------------------
Comparing log10, ^2: (full-variety:regime:term)  VS  (full- variety:temp -variety:regime:term-regime:temp )

```{r}
sq_log10_myfit_4<- lm(sq_log10_leak~variety+regime+temp+variety:regime,
contrasts = c(variety=contr.sum, regime=contr.sum,temp=contr.sum))
anova(sq_log10_myfit_4,sq_log10_myfit_3)
```

According to the p-value log10_myfit_3 does not make difference with log10_myfit_2

```{r}
Anova(sq_log10_myfit_4,type=3)
```

```{r}
qqPlot(sq_log10_myfit_4$residuals, las = 1, main="QQ Plot")
shapiro.test(sq_log10_myfit_4$resid)
plot(sq_log10_myfit_4$fitted,sq_log10_myfit_4$res,xlab="Fitted",ylab="Residuals")
#leveneTest(sq_log10_myfit_2) can not be appy for reduced models
#perform Breusch-Pagan test
bptest(sq_log10_myfit_4)
outlierTest(sq_log10_myfit_4)
```

## Final Model:

sq_log10_leak~variety+regime+temp+variety:regime


```{r}
summary(sq_log10_myfit_4)
```


## Multiple comparison


```{r}
library(lsmeans)
library(multcomp)
comp1<-lsmeans(sq_log10_myfit_4, pairwise ~ variety:regime, adjust="tukey")
plot(comp1$contrasts)
```











